---
output:
  github_document:
    html_preview: false
---

```{r include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)

library(tidyverse)
```

# typer

## Overview

The typer package searches R scripts for type errors. These kinds of errors can be especially difficult to track down because R is a weakly typed language and many functions throw [confusing errors](https://stackoverflow.com/questions/11308367/error-in-my-code-object-of-type-closure-is-not-subsettable) when you pass them an unexpected type.

The `get_type_errors()` function opens an R script and searches for type definitions, which are written using [Roxygen2](http://r-pkgs.had.co.nz/man.html#roxygen-comments) style comments. Then it checks whether types are used consistently throughout the script.

## Installation

```{r eval=FALSE}
devtools::install_github("ngriffiths21/typer")
```

## Usage

First, write type annotations in Roxygen2 comments. Types should be placed in angle brackets at the start of the description of the parameter or return value. Use `class(x)` as the type for `x`.

```{r code=readLines(system.file("example", "simple.R", package = "typer"))}
```

Then run it through the type checker.

```{r message=FALSE}
typer::get_type_errors(system.file("example", "simple.R", package = "typer"))
```

## License

[MIT](https://choosealicense.com/licenses/mit/)
